Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-04-24 manuscript/manuscript.tex
Improved Modified Adaptive Discretization Algorithm in manuscript

From equation \ref{eq:glq-var-dens} we saw that the GLQ approximates 
the volume integrals as the gravitational effect of point masses 
located at the nodes of the quadrature.
If we set the GLQ orders to fixed values, it's easy to conclude that 
the nearer the computation point is to the tesseroid, the accuracy of 
the approximation is reduced and the point masses effect becomes more 
noticeable than the tesseroid we want to approximate.
A complete analysis of this conclusion can be found in \citet{Ku1977, 
Li2011, Uieda2016}.

Studying the homogeneous density tesseroid problem, \citet{Ku1977} 
noticed that keeping the GLQ orders fixed, the approximation 
becomes less accurate when the computation point is closer to the 
tesseroid, making the point masses effect more noticeable than the 
tesseroid we want to approximate.
A complete analysis of this conclusion can be found in \citet{Ku1977, 
Li2011, Uieda2016}.

Instead of increasing the GLQ orders to improve the accuracy, what 
leads to a more time consuming computation, \citet{Li2011} proposed an 
adaptive discretization algorithm which essentially consists in 
dividing the tesseroid based on a ratio between the distance to the 
computation point and its dimensions.
\citet{Uieda2016} proposed a modified version of the algorithm proposed 
by \citet{Li2011}. These modifications can be summed up in:
(1) a faster calculation of the distance from the computation point to 
the tesseroid and 
(2) the application of a stack based algorithm that speeds up the 
computation and gives more control over the recursion step.
More specifically, \citet{Uieda2016} redefined the dimensions of an 
arbitrary tesseroid: $L_\lambda$, $L_\phi$ and $L_r$. The former ones 
are the arc-distances measured along its top surface while $L_r$ is the 
difference between the radii of the top and bottom surfaces.

@@

We will perform similar tests, but now with variable density spherical 
shell.
From the infinite density functions that can be proposed, we have 
chosen three characteristic ones: a linear, an exponential and a 
discontinuous function.
\todo[inline]{sacaria todo este parrafo y lo introduciria mas adelante}

>>>>

Studying the homogeneous density tesseroid problem, \citet{Ku1977} 
noticed that keeping the GLQ orders fixed, the approximation 
becomes less accurate when the computation point is closer to the 
tesseroid, making the point masses effect more noticeable than the 
tesseroid we want to approximate.
One way to prevent this could be increasing the GLQ order in case that 
the computation point is near the tesseroid.
This would uniformly increase the number of point masses inside the 
tesseroid volume.

Instead of doing this, \citet{Li2011} proposed an adaptive 
discretization algorithm which essentially consists in dividing the 
tesseroid based on a ratio between the distance to the computation 
point and its dimensions.
This algorithm produces a more efficient computation because the 
increase of point masses is produced where are more needed.

\citet{Uieda2016} proposed a modified version of this algorithm, whose
modifications can be summed up in:
(1) a faster calculation of the distance from the computation point to 
the tesseroid and 
(2) the application of a stack based algorithm that speeds up the 
computation and gives more control over the recursion step.
More specifically, \citet{Uieda2016} redefined the dimensions of an 
arbitrary tesseroid: $L_\lambda$, $L_\phi$ and $L_r$. The former ones 
are the arc-distances measured along its top surface while $L_r$ is the 
difference between the radii of the top and bottom surfaces.

@@
